Presentation

### 2017-02-14 paper_project2.Rmd
paper commit and slides draft

## Results
### Table
```{r}
# percentages are calculated after excluding missing values
vars <- c("therapysite", "numsessions", "AGE", "year_post_diag", "sex", "bmi", "ethnic", "race", "healthinsurance", "tptotal", "acr_fmness", "CMSI_Total", "BPI_PainSeverity_V2", "BPI_PainSeverity_V3", "BPI_PainSeverity_V4")
cat_vars <- c("initialsite", "grpnbr", "therapysite", "sex", "ethnic", "race", "highesteduc", "relationstatus","currentemployment", "healthinsurance")
tab1 <- CreateTableOne(data = pain, vars = vars, factorVars = cat_vars, strata = "condition")
print(tab1, showAllLevels = T)
```

The modeling strategy employed in this study is dependent on the assumption that all other variables besides treatment type and time were equal between treatment groups. This assumption of equality is based on the randomization scheme used by the study, and is evaluated in Table 1. Table 1 shows several baseline patient measurements, stratified by treatment type. Variables were compared between the treatment groups using chi-squared tests if they were categorical and one-way anova if they were continuous. The normality assumption for the anova tests was evaluated using the density plots in Table 2. Looking at the results from the chi-squared tests and one-way anova tests, with a p-value cutoff of 0.05, there do not seem to be any baseline measurements that differ between the three treatment groups. The only borderline variable is CMSI_Total, with a p-value of 0.050; however, it should be noted that we are doing multiple testing, and that a more conservative cutoff could have been chosen if the priority was to minimize false positives. Note also that while the two therapy sites were expected to have different patient demographics, both treatment sites shared interventionists and supervision coordinators, minimizing site effects beyond the demographic information.

```{r figure 1, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(long_pain, aes(x = pain)) + geom_density() + facet_wrap(condition ~
    time) 
#ggplot(group_pain, aes(x = mean_pain)) + geom_density() + facet_wrap(condition ~ time) 
```

### Group pain
```{r, message=FALSE, warning=FALSE, results="asis", echo = F}
#group <- lmer(mean_pain ~ time + time:condition + (0 + grpnbr | time), data = group_pain)
#summary(group)
#confint(group, method="boot", nsim=1000)
group <- lme(mean_pain ~ time + time:condition, random = ~ 0 + time | grpnbr, data = group_pain)
#summary(group) # this is the one I'm going with I think; I took mean pain for each group, then two levels.
stargazer(group, type = "text", report = "vcsp", header = F, digits = 2)
```
The results from the linear mixed model can be seen in Table 3. The model uses the baseline time point (V2) and the control therapy (EDU) as the reference levels. The coefficients in the model can be interpreted as follows: the timeV coefficients are the difference in mean pain for EDU groups between the respective time V and time V2; the interaction terms timeV:conditionCBT are the difference in mean pain between CBT and EDU groups at the respective timeV; and the interaction terms timeV:conditionEET are the difference in mean pain between EET and EDU groups at the respective timeV. Using a cutoff value of p = 0.05, the model results show that there is a significant decrease in mean pain from time point V2 to time point V4 for the EDU groups. It also shows that at time point V3, EET groups have significantly lower mean pain scores than EDU groups at time point V3. CBT groups at time V3 also have lower mean pain scores than EDU groups, but to a lesser extent than EET groups. By time point V4, there is no discernable difference in mean pain scores between all three groups. Overall, EET and CBT groups decrease in mean pain score between time points V2 and V3, but then do not continue decreasing between time points V3 and V4. Meanwhile, the EDU groups do not decrease in mean pain scores between V2 and V3, but then decrease in mean pain scores between time points V3 and V4, catching up to the mean pain scores for the other groups.

```{r diagnostics, message=FALSE, warning=FALSE, echo = F}
par(mfrow=c(1,1))

p1 <- ggplot() + geom_point(aes(fitted(group), residuals(group, type="normalized"))) + 
  xlab("Fitted Pain Values") +
  ylab("Normalized Residuals") + 
  geom_hline(yintercept = 0) +
  stat_smooth()
  geom_smooth(method = "lm", se = FALSE)
p2 <- qplot(fitted(group), group_pain$mean_pain, xlab = "Fitted Pain Values", ylab = "Actual Pain Values") + geom_abline(slope = 1)
grid.arrange(p1, p2, nrow=1)
```
The residual plots can be seen in Figure 2. Looking at the normalized residual plot, it can be seen that there is a slight positive trend between the fitted pain values and the residuals. On the fitted pain values versus actual pain value plot, the same trend can be seen, but does not appear as impactful.

## Discussion and Conclusion
There did not appear to be any significant differences in baseline demographics between treatment therapies, indicating that the randomization process was successful. Overall, there is a trend of mean pain scores decreasing over time for all three treatments groups, with mean pain score starting around 5.4 at V2 and ending around 4.7 at V4. This overall 13 percent drop does not meet the recommended 30 percent drop, but varies from patient to patient; 52 out of the 230 patients (22 percent) of the patients had a 30 percent or greater decrease in pain.

@@

## Appendix

>>>>

## Results
```{r, message=FALSE, warning=FALSE, echo = F, results = "hide"}
# percentages are calculated after excluding missing values
vars <- c("therapysite", "numsessions", "AGE", "year_post_diag", "sex", "bmi", "ethnic", "race", "healthinsurance", "tptotal", "acr_fmness", "CMSI_Total", "BPI_PainSeverity_V2", "BPI_PainSeverity_V3", "BPI_PainSeverity_V4")
cat_vars <- c("initialsite", "grpnbr", "therapysite", "sex", "ethnic", "race", "highesteduc", "relationstatus","currentemployment", "healthinsurance")
tab1 <- CreateTableOne(data = pain, vars = vars, factorVars = cat_vars, strata = "condition")
tab1mat <- print(tab1, showAllLevels = T)
#write.csv(tab1mat, file = "tableone.csv")
```
\begin{table}[!htbp]
\centering
\begin{tabular}{|l|l|l|l|l|l|}
\hline
 & level & EDU & CBT & EET & p \\ \hline
n &  & 76 & 75 & 79 &  \\ \hline
Therapy site (\%) & UM & 31 (40.8) & 32 (42.7) & 38 (48.1) & 0.634 \\ \hline
 & WSU & 45 (59.2) & 43 (57.3) & 41 (51.9) &  \\ \hline
Number of sessions (mean (sd)) &  & 6.46 (1.65) & 5.93 (2.09) & 6.51 (1.85) & 0.114 \\ \hline
Age (mean (sd)) &  & 50.28 (12.48) & 48.13 (12.54) & 48.98 (11.70) & 0.552 \\ \hline
Years after diagnosis (mean (sd)) &  & 7.36 (8.19) & 8.84 (7.62) & 8.86 (8.08) & 0.426 \\ \hline
Sex (\%) & 1 & 75 (98.7) & 68 (90.7) & 73 (92.4) & 0.094 \\ \hline
 & 2 & 1 ( 1.3) & 7 ( 9.3) & 6 ( 7.6) &  \\ \hline
BMI (mean (sd)) &  & 31.46 (6.37) & 30.16 (7.71) & 29.16 (6.64) & 0.121 \\ \hline
Ethnic (\%) & 1 & 4 ( 5.3) & 2 ( 2.7) & 2 ( 2.6) & 0.601 \\ \hline
 & 2 & 72 (94.7) & 71 (97.3) & 76 (97.4) &  \\ \hline
Race (\%) & 1 & 0 ( 0.0) & 1 ( 1.3) & 1 ( 1.3) & 0.361 \\ \hline
 & 3 & 1 ( 1.3) & 0 ( 0.0) & 0 ( 0.0) &  \\ \hline
 & 4 & 18 (23.7) & 15 (20.0) & 8 (10.1) &  \\ \hline
 & 5 & 54 (71.1) & 57 (76.0) & 68 (86.1) &  \\ \hline
 & 6 & 3 ( 3.9) & 2 ( 2.7) & 2 ( 2.5) &  \\ \hline
Has health insurance (\%) & 0 & 9 (11.8) & 9 (12.0) & 4 ( 5.1) & 0.244 \\ \hline
 & 1 & 67 (88.2) & 66 (88.0) & 75 (94.9) &  \\ \hline
tp total (mean (sd)) &  & 14.75 (2.53) & 14.63 (3.00) & 14.69 (2.77) & 0.963 \\ \hline
acr fmness (mean (sd)) &  & 20.57 (4.73) & 20.34 (4.73) & 20.96 (4.36) & 0.713 \\ \hline
CMSI Total (mean (sd)) &  & 38.76 (12.86) & 34.00 (11.72) & 37.31 (11.74) & 0.050 \\ \hline
Pain at time V2 (mean (sd)) &  & 5.47 (1.74) & 5.35 (1.62) & 5.34 (1.55) & 0.863 \\ \hline
Pain at time V3 (mean (sd)) &  & 5.26 (1.69) & 4.74 (1.66) & 4.42 (2.04) & 0.019 \\ \hline
Pain at time V4 (mean (sd)) &  & 4.86 (1.97) & 4.83 (1.69) & 4.49 (2.20) & 0.462 \\ \hline
Pain difference V2-V4 (mean (sd)) &  & 0.63 (1.92) & 0.57 (1.55) & 0.80 (1.62) & 0.713 \\ \hline
\end{tabular}
\caption{Descriptive statistics by therapy. }
\label{}
Generated p-values are from chi-squared tests if categorical variable and one-way anova if continuous. 
\end{table}

The modeling strategy employed in this study is dependent on the assumption that all other variables besides treatment type and time were equal between treatment groups. This assumption of equality is based on the randomization scheme used by the study, and is evaluated in Table 1. Table 1 shows several baseline patient measurements, stratified by treatment type. Variables were compared between the treatment groups using chi-squared tests if they were categorical and one-way anova if they were continuous. The normality assumption for the anova tests was evaluated using the density plots in Figure 1. Looking at the results from the chi-squared tests and one-way anova tests, with a p-value cutoff of 0.05, there do not seem to be any baseline measurements that differ between the three treatment groups. The only borderline variable is CMSI_Total, with a p-value of 0.050; however, it should be noted that we are doing multiple testing, and that a more conservative cutoff could have been chosen if the priority was to minimize false positives. Note also that while the two therapy sites were expected to have different patient demographics, both treatment sites shared interventionists and supervision coordinators, minimizing site effects beyond the demographic information.

```{r figure 1, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(long_pain, aes(x = pain)) + geom_density() + facet_wrap(condition ~
    time) + ggtitle("Figure 1: Density plots for pain by treatment and time point")
#ggplot(group_pain, aes(x = mean_pain)) + geom_density() + facet_wrap(condition ~ time) 
```

### Model
```{r, message=FALSE, warning=FALSE, results="asis", echo = F}
#group <- lmer(mean_pain ~ time + time:condition + (0 + grpnbr | time), data = group_pain)
#summary(group)
#confint(group, method="boot", nsim=1000)
group <- lme(mean_pain ~ time + time:condition, random = ~ 0 + time | grpnbr, data = group_pain)
#summary(group) # this is the one I'm going with I think; I took mean pain for each group, then two levels.
#stargazer(group, type = "text", report = "vcsp", header = F, digits = 2)
```
\begin{table}[!htbp]
\centering
\begin{tabular}{llll}
\hline
Variable & Value & Std.Error & p-value \\ \hline
timeV3 & -0.22 & 0.22 & 0.30 \\
timeV4 & -0.58 & 0.24 & 0.02 \\
timeV2*conditionCBT & -0.10 & 0.30 & 0.75 \\
timeV3*conditionCBT & -0.56 & 0.32 & 0.09 \\
timeV4*conditionCBT & -0.12 & 0.41 & 0.77 \\
timeV2*conditionEET & -0.13 & 0.29 & 0.66 \\
timeV3*conditionEET & -0.90 & 0.31 & 0.01 \\
timeV4*conditionEET & -0.41 & 0.40 & 0.30
\end{tabular}
\caption{Linear Mixed Model results}
\label{}
 P-values are calcuated using 72 degrees of freedom.
\end{table}

The results from the linear mixed model can be seen in Table 2. The model uses the baseline time point (V2) and the control therapy (EDU) as the reference levels. The coefficients in the model can be interpreted as follows: the timeV coefficients are the difference in mean pain for EDU groups between the respective time V and time V2; the interaction terms timeV:conditionCBT are the difference in mean pain between CBT and EDU groups at the respective timeV; and the interaction terms timeV:conditionEET are the difference in mean pain between EET and EDU groups at the respective timeV. Using a cutoff value of p = 0.05, the model results show that there is a significant decrease in mean pain from time point V2 to time point V4 for the EDU groups. It also shows that at time point V3, EET groups have significantly lower mean pain scores than EDU groups at time point V3. CBT groups at time V3 also have lower mean pain scores than EDU groups, but to a lesser extent than EET groups. By time point V4, there is no discernable difference in mean pain scores between all three groups. Overall, EET and CBT groups decrease in mean pain score between time points V2 and V3, but then do not continue decreasing between time points V3 and V4. Meanwhile, the EDU groups do not decrease in mean pain scores between V2 and V3, but then decrease in mean pain scores between time points V3 and V4, catching up to the mean pain scores for the other groups.

```{r diagnostics, message=FALSE, warning=FALSE, echo = F}
p1 <- ggplot() + geom_point(aes(fitted(group), residuals(group, type="normalized"))) + 
  xlab("Fitted Pain Values") +
  ylab("Normalized Residuals") + 
  geom_hline(yintercept = 0) +
  stat_smooth()
p2 <- qplot(fitted(group), group_pain$mean_pain, xlab = "Fitted Pain Values", ylab = "Actual Pain Values") + geom_abline(slope = 1)
grid.arrange(p1, p2, nrow=1, top = "Figure 2: Residual plots")
```
The residual plots can be seen in Figure 2. Looking at the normalized residual plot, it can be seen that there is a slight positive trend between the fitted pain values and the residuals. On the fitted pain values versus actual pain value plot, the same trend can be seen, but does not appear as impactful.

## Conclusion
Overall, there is a trend of mean pain scores decreasing over time for all three treatments groups, with mean pain score starting around 5.4 at V2 and ending around 4.7 at V4. This overall 13 percent drop does not meet the recommended 30 percent drop, but varies from patient to patient; 52 out of the 230 patients (22 percent) of the patients had a 30 percent or greater decrease in pain.

@@

### 2017-02-14 presentation.Rmd
paper commit and slides draft

---
title: "Presentation"
author: "Dylan Sun"
date: "2/13/2017"
output: html_document
---

### Comparing treatment groups to control groups
```{r}
t.test(pain[condition == "EDU", .(BPI_PainSeverity_V2)], pain[condition == "CBT", .(BPI_PainSeverity_V2)])
t.test(pain[condition == "EDU", .(BPI_PainSeverity_V2)], pain[condition == "EET", .(BPI_PainSeverity_V2)])

t.test(pain[condition == "EDU", .(BPI_PainSeverity_V3)], pain[condition == "CBT", .(BPI_PainSeverity_V3)])
t.test(pain[condition == "EDU", .(BPI_PainSeverity_V3)], pain[condition == "EET", .(BPI_PainSeverity_V3)])

t.test(pain[condition == "EDU", .(BPI_PainSeverity_V4)], pain[condition == "CBT", .(BPI_PainSeverity_V4)])
t.test(pain[condition == "EDU", .(BPI_PainSeverity_V4)], pain[condition == "EET", .(BPI_PainSeverity_V4)])

```
T-tests comparing the difference in mean pain at baseline found no difference between EDU and EET, and no difference between EDU and CBT.

T-tests comparing the difference in mean pain immediately post-treatment found a significant difference between EDU and EET, and a significant difference between EDU and CBT.

T-tests comparing the difference in mean pain six months post-treatment found no difference between EDU and EET, and no difference between EDU and CBT.

>>>>

---
title: "Presentation"
author: "Dylan Sun"
date: "2/13/2017"
output:
  slidy_presentation:
    font_adjustment: 2
---

```{r, message=FALSE, warning=FALSE, echo = F}
# load packages
library(data.table)
library(readxl)
library(lme4)
library(nlme)
library(stargazer)
library(tableone)
library(ggplot2)
library(gridExtra)
```
```{r, message=FALSE, warning=FALSE, results='hide', echo = F}
# load data
full <- read_excel("~/Downloads/Updated DATAforBIOSTAT699.xls")
full <- data.table(full)
full <- full[, year_of_start := gsub("^(\\d{4}).*", "\\1", study_start)]
full <- full[, year_post_diag := as.numeric(year_of_start) - yearfmdiagnosed]
pain <- full[, .(pid, initialsite, condition, grpnbr, numsessions, therapysite, AGE, yearfmonset, yearfmdiagnosed, year_post_diag, sex, bmi, ethnic, race, highesteduc, relationstatus, numberhousehold, numberchildren, currentemployment, hhincome, healthinsurance, tptotal, acr_fmness, CMSI_Total, BPI_PainSeverity_V2, BPI_PainSeverity_V3, BPI_PainSeverity_V4)]
pain[, condition := factor(condition, levels = c("EDU", "CBT", "EET"))]
pain[, pain_diff := BPI_PainSeverity_V2- BPI_PainSeverity_V4]
pain[, pain_diff_pct := (BPI_PainSeverity_V2 - BPI_PainSeverity_V4) / BPI_PainSeverity_V2]

long_pain <- melt(pain, measure.vars = c("BPI_PainSeverity_V2", "BPI_PainSeverity_V3", "BPI_PainSeverity_V4"), variable.name = "time", value.name = "pain")
long_pain[, pain := as.numeric(pain)]
long_pain[time == "BPI_PainSeverity_V2", time := "V2"]
long_pain[time == "BPI_PainSeverity_V3", time := "V3"]
long_pain[time == "BPI_PainSeverity_V4", time := "V4"]
long_pain[, time := factor(time, levels = c("V2", "V3", "V4"))]
long_pain[, grpnbr := as.factor(grpnbr)]
long_pain[, pid := as.numeric(pid)]
long_pain[, condition := factor(condition, levels = c("EDU", "CBT", "EET"))]

group_pain <- long_pain[, .(mean_yrpost_diag = mean(year_post_diag, na.rm = T), mean_age = mean(AGE), mean_pain = mean(pain, na.rm = T)), by = .(grpnbr, condition, time)]

complete <- long_pain[!is.na(pain)]
```

```{r, message=FALSE, warning=FALSE, echo = F, results = "hide"}
# percentages are calculated after excluding missing values
vars <- c("therapysite", "numsessions", "AGE", "year_post_diag", "sex", "bmi", "ethnic", "race", "healthinsurance", "tptotal", "acr_fmness", "CMSI_Total", "BPI_PainSeverity_V2", "BPI_PainSeverity_V3", "BPI_PainSeverity_V4")
cat_vars <- c("initialsite", "grpnbr", "therapysite", "sex", "ethnic", "race", "highesteduc", "relationstatus","currentemployment", "healthinsurance")
tab1 <- CreateTableOne(data = pain, vars = vars, factorVars = cat_vars, strata = "condition")
tab1mat <- print(tab1, showAllLevels = T)
#write.csv(tab1mat, file = "tableone.csv")
```

```{r, message=FALSE, warning=FALSE, results="asis", echo = F}
#group <- lmer(mean_pain ~ time + time:condition + (0 + grpnbr | time), data = group_pain)
#summary(group)
#confint(group, method="boot", nsim=1000)
group <- lme(mean_pain ~ time + time:condition, random = ~ 0 + time | grpnbr, data = group_pain)
#summary(group) # this is the one I'm going with I think; I took mean pain for each group, then two levels.
#stargazer(group, type = "text", report = "vcsp", header = F, digits = 2)
```

## Study Design

## Objectives

## Descriptives
|  	| level 	| EDU 	| CBT 	| EET 	| p 	|
|-----------------------------------	|-------	|---------------	|---------------	|---------------	|-------	|
| n 	|  	| 76 	| 75 	| 79 	|  	|
| Therapy site (\%) 	| UM 	| 31 (40.8) 	| 32 (42.7) 	| 38 (48.1) 	| 0.634 	|
|  	| WSU 	| 45 (59.2) 	| 43 (57.3) 	| 41 (51.9) 	|  	|
| Number of sessions (mean (sd)) 	|  	| 6.46 (1.65) 	| 5.93 (2.09) 	| 6.51 (1.85) 	| 0.114 	|
| Age (mean (sd)) 	|  	| 50.28 (12.48) 	| 48.13 (12.54) 	| 48.98 (11.70) 	| 0.552 	|
| Years after diagnosis (mean (sd)) 	|  	| 7.36 (8.19) 	| 8.84 (7.62) 	| 8.86 (8.08) 	| 0.426 	|
| Sex (\%) 	| 1 	| 75 (98.7) 	| 68 (90.7) 	| 73 (92.4) 	| 0.094 	|
|  	| 2 	| 1 ( 1.3) 	| 7 ( 9.3) 	| 6 ( 7.6) 	|  	|
| BMI (mean (sd)) 	|  	| 31.46 (6.37) 	| 30.16 (7.71) 	| 29.16 (6.64) 	| 0.121 	|
| Ethnic (\%) 	| 1 	| 4 ( 5.3) 	| 2 ( 2.7) 	| 2 ( 2.6) 	| 0.601 	|
|  	| 2 	| 72 (94.7) 	| 71 (97.3) 	| 76 (97.4) 	|  	|
| Race (\%) 	| 1 	| 0 ( 0.0) 	| 1 ( 1.3) 	| 1 ( 1.3) 	| 0.361 	|
|  	| 3 	| 1 ( 1.3) 	| 0 ( 0.0) 	| 0 ( 0.0) 	|  	|
|  	| 4 	| 18 (23.7) 	| 15 (20.0) 	| 8 (10.1) 	|  	|
|  	| 5 	| 54 (71.1) 	| 57 (76.0) 	| 68 (86.1) 	|  	|
|  	| 6 	| 3 ( 3.9) 	| 2 ( 2.7) 	| 2 ( 2.5) 	|  	|
| Has health insurance (\%) 	| 0 	| 9 (11.8) 	| 9 (12.0) 	| 4 ( 5.1) 	| 0.244 	|
|  	| 1 	| 67 (88.2) 	| 66 (88.0) 	| 75 (94.9) 	|  	|
| tp total (mean (sd)) 	|  	| 14.75 (2.53) 	| 14.63 (3.00) 	| 14.69 (2.77) 	| 0.963 	|
| acr fmness (mean (sd)) 	|  	| 20.57 (4.73) 	| 20.34 (4.73) 	| 20.96 (4.36) 	| 0.713 	|
| CMSI Total (mean (sd)) 	|  	| 38.76 (12.86) 	| 34.00 (11.72) 	| 37.31 (11.74) 	| 0.050 	|
| Pain at time V2 (mean (sd)) 	|  	| 5.47 (1.74) 	| 5.35 (1.62) 	| 5.34 (1.55) 	| 0.863 	|
| Pain at time V3 (mean (sd)) 	|  	| 5.26 (1.69) 	| 4.74 (1.66) 	| 4.42 (2.04) 	| 0.019 	|
| Pain at time V4 (mean (sd)) 	|  	| 4.86 (1.97) 	| 4.83 (1.69) 	| 4.49 (2.20) 	| 0.462 	|
| Pain difference V2-V4 (mean (sd)) 	|  	| 0.63 (1.92) 	| 0.57 (1.55) 	| 0.80 (1.62) 	| 0.713 	|

## Normality
```{r figure 1, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(long_pain, aes(x = pain)) + geom_density() + facet_wrap(condition ~
    time) + ggtitle("Figure 1: Density plots for pain by treatment and time point")
#ggplot(group_pain, aes(x = mean_pain)) + geom_density() + facet_wrap(condition ~ time) 
```

## Model

## Model results
| Variable            | Value     | Std.Error | p-value |
|---------------------|-----------|-----------|---------|
| timeV3              | -0.223214 | 0.2154765 | 0.3037  |
| timeV4              | -0.576035 | 0.2365247 | 0.0174  |
| timeV2*conditionCBT | -0.097448 | 0.2986305 | 0.7451  |
| timeV3*conditionCBT | -0.557840 | 0.3235078 | 0.0889  |
| timeV4*conditionCBT | -0.120446 | 0.4105077 | 0.7701  |
| timeV2*conditionEET | -0.125255 | 0.2869149 | 0.6637  |
| timeV3*conditionEET | -0.900893 | 0.3108163 | 0.0050  |
| timeV4*conditionEET | -0.411253 | 0.3944031 | 0.3006  |

## Model diagnostics
```{r diagnostics, message=FALSE, warning=FALSE, echo = F}
p1 <- ggplot() + geom_point(aes(fitted(group), residuals(group, type="normalized"))) + 
  xlab("Fitted Pain Values") +
  ylab("Normalized Residuals") + 
  geom_hline(yintercept = 0) +
  stat_smooth()
p2 <- qplot(fitted(group), group_pain$mean_pain, xlab = "Fitted Pain Values", ylab = "Actual Pain Values") + geom_abline(slope = 1)
grid.arrange(p1, p2, nrow=1, top = "Figure 2: Residual plots")
```

## Conclusions
